Incentivizing Exploration with Unbiased History

### 2018-11-02 intro-intro.tex
added a comment.

>>>>

\ascomment{Nicole: It would be good to introduce "disclosure policy" (= online algorithm that chooses messages, in the context of incentivizing exploration). And also talk about recommendation system as smth that exists regardless of incentivizing exploration, and is very common/important out there.}
